---
authors:
- admin
date: "2019-11-23"
draft: false
gallery_item:
image:
  caption: ''
  focal_point: "center"
  preview_only: false
lastmod: "2019-11-23T00:00:00-08:00"
summary:  
projects:
tags:
- R
url_slides: "https://github.com/laRusers/socalr2019"
title: 'SoCal All Hands useR Meeting Twitter Blog'
subtitle: "An entire day of R fun with R Users Groups and R-Ladies"
---


## Please check out all the slides [here](https://github.com/laRusers/socalr2019).

##### Workshops by [Malcolm Barrett](https://twitter.com/malco_barrett) and [Emil Hvitfeldt](https://twitter.com/Emil_Hvitfeldt)

<center>
```{r echo=FALSE}
blogdown::shortcodes('tweet', c('1198327578685100032',
                                '1198444110081736704',
                                '1198357797433303040',
                                '1198444940717543424',
                                '1198440420117598208'))
```

##### "Software Engineering with Shiny" by [Alan Dipert](https://twitter.com/alandipert)
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198377866578120704')
blogdown::shortcode('tweet', '1198333013571989504')

```

##### "Artificial Intelligence & Analytical Innovation" by [Qinghua Song](https://www.linkedin.com/in/song-qinghua-40352b12/)
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198381621059018752')
```

##### "Staying clean and DRY - best practices for code reuse and collaboration" by [Peter Foley](https://www.linkedin.com/in/peter-foley-6600482/)	
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198378572039122944')
```


##### "Exploring communities with ‘vegan’ - an introduction to community analysis" by [An Bui](https://twitter.com/_anbui)
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198386439190241282')
blogdown::shortcode('tweet', '1198371505295331328')
```


##### "The Linear Algebra Behind Machine Learning: Under the Hood with Regression Analysis" by [Steven Slezak](https://www.linkedin.com/in/steven-slezak-a3243914/)
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198373995600433153')
```

##### "Macgyvering with R: Creating a Work Schedule" by [Wendy Christensen](https://twitter.com/wchristensen)	
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198376779431342080')
```

##### "Condition System in R" by [John Peach](https://www.linkedin.com/in/jpeach/)
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198378164080132096')
```


##### "R for better science in less time" by [Julia Stewart Lowndes](https://twitter.com/juliesquid)
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198395159701901312')
blogdown::shortcode('tweet', '1198385565160202240')
blogdown::shortcode('tweet', '1198384157983793152')
blogdown::shortcode('tweet', '1198393837913198592')
blogdown::shortcode('tweet', '1198466004822548481')
```


##### Future events by [the Orange County R Users Group](https://ocrug.org/)
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198390865166618631')
```


##### Happy memories posted by RLadies SoCal
<center>
```{r echo=FALSE}
blogdown::shortcode('tweet', '1198395337867575296')
blogdown::shortcode('tweet', '1198448792825036800')
blogdown::shortcode('tweet', '1198447535301357570')
```


